---
title: "skew - boundSkew1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
source('../01_graph_skew.R')
```

## Degree of Skewness
```{r skewness, echo = FALSE, fig.align = 'center'}
p1
```

#### With an increase in skewness from weak to strong, gamble acceptance _increases._

```{r baseline, echo = FALSE} 
base <- readRDS('../output/baseline.RDS')
knitr::kable(summary(base)$coefficients) %>% 
  kable_styling(full_width = F) %>%
  row_spec(3:4, bold = T, background = 'yellow')
```

## Valence
```{r valence, echo = FALSE, fig.align = 'center'}
p4
```

#### The acceptance rates for moderate- and strongly-skewed gambles is greater than symmtetric or weakly-skewed gambles, but this is moderated by valence. Gamble acceptance is similar for all gambles in the loss domain.

```{r m1, echo = FALSE} 
m1 <- readRDS('../output/m1.RDS')
knitr::kable(summary(m1)$coefficients) %>% 
  kable_styling(full_width = F) %>%
  row_spec(c(3:4,11:12), bold = T, background = 'yellow')
```

## Magnitude
```{r magnitude, echo = FALSE, fig.align = 'center'}
p5
```

#### Again, the acceptance rates for moderate- and strongly-skewed gambles is greater than symmtetric or weakly-skewed gambles, but this is moderated by magnitude. Gamble acceptance is similar for all high magnitude (EV = /$5) gambles.

```{r m2, echo = FALSE} 
m2 <- readRDS('../output/m2.RDS')
knitr::kable(summary(m2)$coefficients) %>% 
  kable_styling(full_width = F) %>%
  row_spec(c(3:4,11:12), bold = T, background = 'yellow')
```

## Magnitude and valence

#### Although a model containing the interaction between magnitude and valence (m3) provides a better fit to the data than a model with valence alone (m1), the model results are somewhat difficult to interpret. 

``` {r model compare, echo = FALSE}
m1 <- readRDS('../output/m1.RDS')
m3 <- readRDS('../output/m3.RDS')
knitr::kable(anova(m1, m3)) %>% 
  kable_styling(full_width = F) 
```

#### Again, the acceptance rates for moderate- and strongly-skewed gambles is greater than symmtetric or weakly-skewed gambles. However, for losses of \$5 does not fit this pattern; here skewed gambles are accepted less than symmetric. Futher, for gains of \$5, moderately-skewed gambles are accepted less than strongly-skewed gambles.

```{r mag and val, echo = FALSE, fig.align = 'center'}
p2
```


```{r model 3, echo = FALSE} 
m3 <- readRDS('../output/m3.RDS')
knitr::kable(summary(m3)$coefficients) %>% 
  kable_styling(full_width = F) %>%
  row_spec(11, bold = T, background = 'yellow') %>%
  row_spec(c(3:4,9:11,19), bold = T, background = 'yellow')
```