---
title: "Individual Differences - boundSkew1"
author: "Kendra Seaman"
date: "12/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('../09_individual_differences.R')
library(kableExtra)
library(ggplot2)
```

## Correlations with Acceptance of Skewed Gambles

```{r correlations, echo = FALSE}
ctable <- readRDS('../output/s1_corrCI.RDS')
knitr::kable(ctable[2:nrow(ctable),1:2])  %>% 
  kable_styling(full_width = F) %>%
  row_spec(c(1,3:4, 6, 13:14, 17:18), bold = T, background = 'yellow')
```

### "I tried to solve the task on a gut level."
```{r graph gut, echo = FALSE}
ggplot(d7, aes(gut, skew_count)) + theme_minimal() +
  geom_jitter(alpha=0.2, width = 0.2, height = 0.2) +
  geom_smooth(method = lm, color = 'blue', fill = 'blue' ) + 
  scale_y_continuous(breaks=seq(0,9,3))
```

### "I tried to solve the task by focusing on how much money I could win."
```{r graph win.money, echo = FALSE}
ggplot(d7, aes(win.money, skew_count)) + theme_minimal() +
  geom_jitter(alpha=0.2, width = 0.2, height = 0.2) +
  geom_smooth(method = lm, color = 'blue', fill = 'blue' ) + 
  scale_y_continuous(breaks=seq(0,9,3))
```

### "I tried to solve the task by focusing on how much money I could lose."
```{r graph lose.money, echo = FALSE}
ggplot(d7, aes(lose.money, skew_count)) + theme_minimal() +
  geom_jitter(alpha=0.2, width = 0.2, height = 0.2) +
  geom_smooth(method = lm, color = 'blue', fill = 'blue' ) + 
  scale_y_continuous(breaks=seq(0,9,3))
```

### "I tried to solve the task by focusing on how likely it was that I would lose."
```{r graph lose.likely, echo = FALSE}
ggplot(d7, aes(lose.likely, skew_count)) + theme_minimal() +
  geom_jitter(alpha=0.2, width = 0.2, height = 0.2) +
  geom_smooth(method = lm, color = 'blue', fill = 'blue' ) + 
  scale_y_continuous(breaks=seq(0,9,3))
```

### Subjective Graph Literacy
```{r graph sgl, echo = FALSE}
ggplot(d7, aes(graph_lit, skew_count)) + theme_minimal() +
  geom_jitter(alpha=0.2, width = 0.2, height = 0.2) +
  geom_smooth(method = lm, color = 'blue', fill = 'blue' ) + 
  scale_y_continuous(breaks=seq(0,9,3))
```

### Numeracy
```{r graph numeracy, echo = FALSE}
ggplot(d7, aes(Numeracy, skew_count)) + theme_minimal() +
  geom_jitter(alpha=0.2, width = 0.2, height = 0.2) +
  geom_smooth(method = lm, color = 'blue', fill = 'blue' ) + 
  scale_y_continuous(breaks=seq(0,9,3))
```

### "How likely are you to make a fraudulent investment?"
```{r graph likely_fraud, echo = FALSE}
ggplot(d7, aes(likely_fraud, skew_count)) + theme_minimal() +
  geom_jitter(alpha=0.2, width = 0.2, height = 0.2) +
  geom_smooth(method = lm, color = 'blue', fill = 'blue' ) + 
  scale_y_continuous(breaks=seq(0,9,3))
```

### How able are you to resist high-pressure sales tactics when buying investments?"
```{r graph high_pressure, echo = FALSE}
ggplot(d7, aes(high_pressure, skew_count)) + theme_minimal() +
  geom_jitter(alpha=0.2, width = 0.2, height = 0.2) +
  geom_smooth(method = lm, color = 'blue', fill = 'blue' ) + 
  scale_y_continuous(breaks=seq(0,9,3))
```